### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

\section{Side-channel Attacks}
Side channels can leak sensitive information
unconsciously through different execution behaviors caused by shared 
hardware components (e.g., CPU cache, TLB, and
DRAM) in modern computer systems~\cite{ge2018survey,szefer2019survey}.

@@

Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

>>>>

\section{Side-channel Attacks}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

Side channels can leak sensitive information
unconsciously through different execution behaviors caused by shared 
hardware components (e.g., CPU cache, TLB, and
DRAM) in modern computer system~\cite{ge2018survey,szefer2019survey}.

@@
